A First Effort for a Distributed Segment-based Approach on Topology-agnostic Self-Assembled Nano Networks

### 2013-09-18 trunk/PAPER/paper.tex
Added conclusion and fixed intro

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale, topology agnostic
scenario based on DNA self-assembly. The main aim is exploiting the
already-proven qualities of segment-based routing without neither requiring a
topology graph as input, nor needing a centralized algorithm to
configure network paths. 
After introducing the conceptual elements and the execution model of
DiSR, we developed the opensource Nanoxim tool to show how the proposed
approach can be used to discover irregular network topology while
estabilishing network segments.  The results shows how DiSR still
preserves some important features
(connectivity, defect tolerance, scalability)  while avoiding centralized
tree-based broadcasting and resource hungry solutions such as virtual
channels and hardware redundancy. Finally, we analyzed a possible
VHDL hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 15 to
about 25\% of the budget of transistors available for each node.
\end{abstract}

@@

\section{Conclusions}
...

>>>>

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale,
topology agnostic scenario based on DNA self-assembly. The main aim is
exploiting the already-proven qualities of segment-based routing
without neither requiring a topology graph as input, nor needing a
centralized algorithm to configure network paths.  After introducing
the conceptual elements and the execution model of DiSR, we show how
the opensource Nanoxim platform has been used to evaluate the proposed
approach in the process of discovering irregular network topology
while estabilishing network segments.  Results show how DiSR still
preserves some important properties (coverage, defect tolerance,
scalability)  while avoiding centralized tree-based broadcasting and
resource hungry solutions such as virtual channels and hardware
redundancy. Finally, we analyzed a first, not yet optimised VHDL
hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 15 to
about 25\% of the budget of transistors available for each node.
\end{abstract}

@@

\section{Conclusions}
In this work we presented DiSR, a initial attempt of porting a segment based
approach to distributed self-assembled nanoscale scenario. We
demostrated how DiSR can accomplish the aim of finding a segment
coverage of the network withouth requiring any centralized approach
that would request a graph topology as input. A draft hardware
implementation has been presented to evalute the impact on the limited
node size typical of the assumed scenario. Future works will focus on
developing self tuning of DiSR to match a high coverage levels and the
detailed low level hardware implementation on
DNA grid using the appropriate nano devices models.
